### 2024-10-06 common/characteristic.tex
Remove \sloppy usage from characteristic
it may cause something unpredicted: https://tex.stackexchange.com/a/241355

        \arabic{citeauthorvak} из которых изданы в журналах, рекомендованных ВАК\sloppy%

@@

            , \arabic{citeauthorscopuswos} "--- в~периодических научных журналах, индексируемых Web of~Science и Scopus\sloppy%

@@

            \formbytotal{citeauthorpatent}{патент}{}{а}{}\sloppy%

>>>>

        \arabic{citeauthorvak} из которых изданы в журналах, рекомендованных ВАК%

@@

            , \arabic{citeauthorscopuswos} "--- в~периодических научных журналах, индексируемых Web of~Science и Scopus%

@@

            \formbytotal{citeauthorpatent}{патент}{}{а}{}%
